Plots for Latent Hawkes Paper

### 2020-12-04 output_scripts/Paper_Plots.Rmd
move numbers for 5b further away from axis

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=6,fig.width=8}
sim_data_path <- "../output/sims/sims_m3_dc/"

@@

```{r prepare data for 4b,cache=TRUE}
plot.s <- 1#7#9
plot.i <- 4
plot.j <- 5

@@

load(paste0(sim_data_path, "sim_model3_",
                               plot.s,
                              ".RData"))
test.mmhp <- sim_model3_data$mmhp_matrix[plot.i,plot.j][[1]]
temp.t <- test.mmhp$tau
current.n <- length(temp.t)-1
time.segment <- seq(0, tail(temp.t,1), length.out = 5000)

@@

## then need to load in the state estimate here
load(paste0(sim_data_path, "fit123_state_est_", plot.s, ".RData"))

@@

cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
                                 "True")) %>%
  arrange(factor(method, levels = c("C-HP","C-DCHP","C-MMHP","True"))) %>%
  pull(cols)
#load("../output/sim_model3_fit123_residuals.RData")
par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04, 
                col = cols_plot[1], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,
                col = cols_plot[2], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,
                col = cols_plot[3], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,
                col = cols_plot[4], border = NA)
        text(c(0.43,0.58,0.61,0.4), seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      PR <- c(KS_model1_array[,i,j], KS_model2_array[,i,j],
              KS_model3_array[,i,j], KS_true_array[,i,j])
      ### try pr scores instead
      # PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
      #         PR_model3_array[,i,j],PR_true_array[,i,j])
      Type <- c(rep(1,n_sim), rep(2,n_sim), rep(3,n_sim), rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")
      #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)
mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

>>>>

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=6,fig.width=8}
sim_data_path <- "../output/sims_m3_update/"

@@

```{r prepare data for 4b,cache=TRUE}
plot.s <- 6#7#9
plot.i <- 4
plot.j <- 5

@@

load(paste0(sim_data_path,"/" ,"sim_model3_",
                               plot.s,
                              ".RData"))
test.mmhp <- sim_model3_data$mmhp_matrix[plot.i,plot.j][[1]]
temp.t <- test.mmhp$tau
current.n <- length(temp.t)-1
time.segment <- seq(0, tail(temp.t,1), length.out = 5000)

@@

## then need to load in the state estimate here
load(paste0(sim_data_path,"/", "fit123_state_est_", plot.s, ".RData"))

@@

cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
                                 "True")) %>%
  arrange(factor(method, levels = c("C-HP","C-DCHP","C-MMHP","True"))) %>%
  pull(cols)
#load("../output/sim_model3_fit123_residuals.RData")
par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04, 
                col = cols_plot[1], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,
                col = cols_plot[2], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,
                col = cols_plot[3], border = NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,
                col = cols_plot[4], border = NA)
        text(c(0.43,0.58,0.61,0.4), seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      PR <- c(KS_model1_array[,i,j], KS_model2_array[,i,j],
              KS_model3_array[,i,j], KS_true_array[,i,j])
      ### try pr scores instead
      # PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
      #         PR_model3_array[,i,j],PR_true_array[,i,j])
      Type <- c(rep(1,n_sim), rep(2,n_sim), rep(3,n_sim), rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")
      #names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(5:1), side=1, line=1.5, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)
mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)
